How cryptic is cryptic diversity? Machine learning approaches to fine scale variation in the morphology of \textit{Emys marmorata}.

### 2013-05-07 documents/turtle_presentation.Rnw
spatial component

<<>>=
# need to format all the map data so it plays nicely
correct.map <- function(data) {
  out <- lapply(data, 
                function(x) {
                  x$long <- as.numeric(as.character(x$long)) * -1
                  x$lat <- as.numeric(as.character(x$lat))
                  x})

  out
}

map <- map_data('state')
st <- c('california', 'oregon', 'washington')
map <- map[map$region == st, ]

turtle.train <- correct.map(turtle.train)
turtle.test <- correct.map(turtle.test)
adult.train <- correct.map(adult.train)
adult.test <- correct.map(adult.test)

>>>>

<<>>=
# need to format all the map data so it plays nicely
map <- map_data('state')
st <- c('california', 'oregon', 'washington')
map <- map[map$region == st, ]
